Global Warming Distributed Data Analysis

### 2016-03-28 report/article.tex
Figura minima temperatura globale

By using the interactive map it is possible to notice an increase of avarage temperature in Europe and in Asia in the years from 1970 to the current years. In figure \ref{img:increaseMap} it is possible to see an example of increase between the two interval 1976/1980 to 2011/2015. The red colors are dominant in all the figure. Showing an increase of at least 2.5 degrees for all the regions that have a red square over them.

@@

>>>>

By using the interactive map it is possible to notice an increase of the global temperature in the years from 1975 to the current years. In figure \ref{img:increaseMap} it is possible to see an example of increase of the average temperature between the two interval 1976/1980 to 2011/2015 in Europe and in Asia. The red colors are dominant in all the figure. Showing an increase of at least 2.5 degrees for all the regions that have a red square over them.
In figure \ref{img:increaseGlobal} it is possible to see how the minimum temperature is increased for the same two intervals of years in the majority of regions of the world.

@@

\begin{figure}[tbh]
\includegraphics[width=1\linewidth]{increaseGlobal}
\caption{Map that shows the increase of the minimum temperature globally between 1976 and 2015.}
\label{fig:interface}
\end{figure}
